---
title: "AACN Survey - 2022"
subtitle: "Associations"
date: "`r format(Sys.time(), '%B, %Y')`"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

```{r include=FALSE}
# Libraries ---------------------------------------------------------------

library(gtsummary)
library(haven)
library(labelled)
library(flextable)
library(glue)
library(tidyverse)

# Setup -------------------------------------------------------------------

source("00-variable_info.R", local = TRUE)
source("00-helper_functions.R", local = TRUE)

gtsummary::set_gtsummary_theme(theme_gtsummary)

flextable::set_flextable_defaults(
  table.layout = "autofit"
)

dta <- readRDS("data/raw_cleaned.rds")

labels <- labelled::var_label(dta)


missing_removed <- readxl::read_xlsx("AACN_survey-missing_values.xlsx", sheet = "MissingRemoved")

dta <- dta %>% filter(id %in% missing_removed$Responseid)

# in case Respect by variables are shown independenly
new_respect_labs <- labels[vars_respect_by] %>%  map(~ paste0("Respect by:", .))

new_comm_labs <- labels[vars_communication] %>%  map(~ paste0(., " rated Good or Excellent"))

```



## Association of `C17. On the whole, how satisfied are you with your current job?` & `C18. Do you plan to leave your present nursing position?`


-	C17 with c18


<br>

```{r}

dta %>%
  filter(section == "Section C") %>%
  select(satisfied_overall, plan_leave ) %>%
  mutate(
    across(where(is.labelled), as_factor)
  ) %>% 
  set_variable_labels(.labels = labels[names(.)] ) %>%
  tbl_summary(
    by = plan_leave,
    missing = "no"
    # percent = "row"
  ) %>%
  add_overall() %>% 
  add_p(
    test = list(all_categorical() ~ "chisq.test")
  ) %>%
  modify_header(label = " ") %>% 
  modify_caption(
    "Association between Current Job Satisfaction and Intention to Leave") %>%
  modify_spanning_header( all_stat_cols() ~ labels$plan_leave )
```


<br>


## Association of Demographics Vs C17. On the whole, how satisfied are you with your current job?

-	C17 with D1, D4, D5, D6, D7, D8, D9

```{r}

dta %>%
  filter(section == "Section C") %>%
  select(satisfied_overall, 
         # demo
         gender, position, experience, 
         experience_icu,  icu_type, country
  ) %>%
  mutate(
    across(where(is.labelled), as_factor)
  ) %>% 
  set_variable_labels(.labels = labels[names(.)]
                      #plan_leave = "Intention to leave within 1 or 3 years"
  ) %>%
  tbl_summary(
    by = satisfied_overall,
    missing = "no",
    percent = "row"
  ) %>%
  add_p(
    test = list(all_categorical() ~ "chisq.test")
  ) %>% 
  add_overall() %>% 
  modify_header(all_stat_cols() ~ "**{level}**", label = " ") %>% 
  modify_caption(
    "Associations between Demographics and Intention to Leave") %>% 
  modify_spanning_header(
    all_stat_cols() ~ labels$satisfied_overall
  ) 

```

<br>


## Association of Demographics Vs C18. Do you plan to leave your present nursing position?

-	C18 with D1, D4, D5, D6, D7, D8, D9


<br>


```{r}

dta %>%
  filter( section == "Section C" ) %>%
  select( plan_leave, gender, position, experience, experience_icu,  icu_type, country ) %>%
  mutate( across(where(is.labelled), as_factor) ) %>% 
  set_variable_labels( .labels = labels[names(.)] ) %>%
  tbl_summary( by = plan_leave, missing = "no", percent = "row" ) %>%
  add_p( test = list(all_categorical() ~ "chisq.test") ) %>% 
  #modify_header(label = " ") %>% 
  modify_caption( "Associations between Demographics and Intention to Leave" ) %>% 
  modify_spanning_header( all_stat_cols() ~ labels$plan_leave ) 

```


## Association of Demographics Vs C18a. How likely would each of the following be to influence you to reconsider your plans to leave your present position? 

-	C18a with D1, D4, D5, D6, D7, D8, D9


Responses to eleven (11) questions, were in the range of __Very likely, Somewhat likely, Not very likely__ and __Not likely at all__. The associations were performed on the event of response of __Very Likely__ to be influenced by the said factor.


```{r include=FALSE}
by_demo1 <- function(dta, demo_var){
  
  out <- dta %>% 
    filter(section == "Section C") %>%
    select( starts_with("influence_"), {{demo_var}} ) %>% 
    mutate( across(starts_with("influence_"), ~if_else(. == 1, 1, 0)) ) %>% 
    mutate(across(where(is.labelled), as_factor)) %>% 
    set_variable_labels(.labels = labels[names(.)]) %>% 
    tbl_summary( by = {{demo_var}}, missing = "no" ) %>%
    add_p( test = list(all_categorical() ~ "chisq.test") ) %>% 
    modify_header(label = "Very likely to be influenced by:") %>% 
    modify_caption( "Associations between Demographics and 'How likely would each of the following be to influence you to reconsider your plans to leave your present position?'") 
  
  temp <- deparse(substitute(demo_var))
  out %>% 
    modify_spanning_header( all_stat_cols() ~ labels[[temp]] ) 
  
}


```

<br>

### Gender 

<br>

```{r}
by_demo1(dta, gender)

```
<br>

### Current position 

<br>

```{r}
by_demo1(dta, position)

```
<br>

### Place of current work 

<br>

```{r}
by_demo1(dta, workplace)

```
<br>

### Type of ICU 

<br>

```{r}
by_demo1(dta, icu_type)

```
<br>

### Country 

<br>

```{r}
by_demo1(dta, country)

```

<br>

### Years of Experience (Nursing / ICU)

<br>

```{r}
t1 <- dta %>% 
  filter(section == "Section C") %>%
  tbl_cross_correlation(starts_with("influence_"), experience)

t2 <- dta %>% 
  filter(section == "Section C") %>%
  tbl_cross_correlation(starts_with("influence_"), experience_icu)

left_join(t1, t2) %>% 
  rename("Likelihood of influenced by:" = colsx) %>% 
  flextable() %>% 
  flextable::add_header_row(
    values = c("", 
               "Correlation with"), 
    colwidths = c(1,2)
  ) %>% 
  add_footer_row(
    values = c("Note: Spearman correlation coefficient (r). 
               * p < 0.05, ** p < 0.01 "), 
    colwidths = c(3) 
  ) %>% 
  set_caption(
    "Correlation between  `How likely would each of the following be to influence you to reconsider your plans to leave your present position?` and `Years of Experience (Nursing / ICU)`")

```



## Associations A1, A3, A5, A 6 with C17. On the whole, how satisfied are you with your current job?


<br>


```{r}
dta %>% 
  filter(section == "Section C") %>% 
  select(
    implement_hwes_unit, implement_hwes_org, satisfied_nurse, quality_care,
    satisfied_overall
  ) %>% 
  mutate(across(where(is.labelled), as_factor),
         quality_care = fct_drop(quality_care)) %>% 
  tbl_summary( by = satisfied_overall,
               missing = "no",
               percent = "row"
  ) %>% 
  add_overall() %>% 
  add_p( test = list(all_categorical() ~ "chisq.test") ) %>% 
  modify_header(all_stat_cols() ~ "**{level}**",label = "**Healthy Work Environment**") %>% 
  modify_caption( "Associations of 'How satisfied are you with your current job' and ' Implementation of HWE standards' " ) %>% 
  modify_spanning_header( all_stat_cols() ~ labels$satisfied_overall ) 

# Correlations
# dta %>% 
#   filter(section == "Section C") %>%
#   tbl_cross_correlation(c(satisfied_nurse, quality_care), satisfied_overall) %>% 
#   rename(" " = colsx) %>% 
#   flextable()

```


## Associations of A1, A3, A5, A 6 with C18. Do you plan to leave your present nursing position?


<br>


```{r}
dta %>% 
  filter(section == "Section C") %>% 
  select(
    implement_hwes_unit, implement_hwes_org, satisfied_nurse, quality_care,
    plan_leave
  ) %>% 
  mutate(across(where(is.labelled), as_factor),
         quality_care = fct_drop(quality_care)
  ) %>% 
  tbl_summary( by = plan_leave,
               missing = "no",
               percent = "row"
  ) %>% 
  add_overall() %>% 
  add_p( test = list(all_categorical() ~ "chisq.test") ) %>% 
  modify_header(all_stat_cols() ~ "**{level}**",label = "**Healthy Work Environment**") %>% 
  modify_caption( "Associations of 'Intention to leave' and ' Implementation of HWE standards' " ) %>% 
  modify_spanning_header( all_stat_cols() ~ labels$plan_leave ) 

```



## Section B with  C17, C18

<br>

### C17 "On the whole, how satisfied are you with your current job?"

- Organisation 

```{r}

dta %>% 
  select(all_of(dim__scales_org), satisfied_overall) %>% 
  mutate(across(where(is.labelled), as_factor)) %>% 
  tbl_summary( by = satisfied_overall,
               type = everything()~"continuous",
               missing = "no"
               ) %>% 
  add_p() %>% 
    modify_header(label = "**Healthy Work Environment in the Organisation**") %>% 
  modify_caption( "Associations of 'Healthy Work Environment Standards in Organisation' and 'How satisfied are you with your current job' " ) %>% 
  modify_spanning_header( all_stat_cols() ~ labels$satisfied_overall ) 


```


- Unit 


```{r}

dta %>% 
  select(all_of(dim__scales_unit), satisfied_overall) %>% 
  mutate(across(where(is.labelled), as_factor)) %>% 
  tbl_summary( by = satisfied_overall,
               type = everything()~"continuous",
               missing = "no"
               ) %>% 
  add_p() %>% 
    modify_header(label = "**Healthy Work Environment in the Unit**") %>% 
  modify_caption( "Associations of 'Healthy Work Environment Standards in Unit' and 'How satisfied are you with your current job' " ) %>% 
  modify_spanning_header( all_stat_cols() ~ labels$satisfied_overall ) 


```

<br>

### C18 "Do you plan to leave your present nursing position?"

- Organisation 

```{r}

dta %>% 
  select(all_of(dim__scales_org), plan_leave) %>% 
  mutate(across(where(is.labelled), as_factor)) %>% 
  tbl_summary( by = plan_leave,
               type = everything()~"continuous",
               missing = "no"
               ) %>% 
  add_p() %>% 
    modify_header(label = "**Healthy Work Environment in the Organisation**") %>% 
  modify_caption( "Associations of 'Healthy Work Environment Standards in Organisation' and 'Do you plan to leave your present nursing position' " ) %>% 
  modify_spanning_header( all_stat_cols() ~ labels$plan_leave ) 


```


- Unit 


```{r}

dta %>% 
  select(all_of(dim__scales_unit), plan_leave) %>% 
  mutate(across(where(is.labelled), as_factor)) %>% 
  tbl_summary( by = plan_leave,
               type = everything()~"continuous",
               missing = "no"
               ) %>% 
  add_p() %>% 
    modify_header(label = "**Healthy Work Environment in the Unit**") %>% 
  modify_caption( "Associations of 'Healthy Work Environment Standards in Unit' and 'Do you plan to leave your present nursing position' " ) %>% 
  modify_spanning_header( all_stat_cols() ~ labels$plan_leave ) 


```


## Section B with A1, A2, A3,

### A1. Independent of your present job how satisfied are you with being a registered nurse?

- Organisation 

```{r}

dta %>% 
  select(all_of(dim__scales_org), satisfied_nurse) %>% 
  mutate(across(where(is.labelled), as_factor)) %>% 
  tbl_summary( by = satisfied_nurse,
               type = everything()~"continuous",
               missing = "no"
               ) %>% 
  add_p() %>% 
    modify_header(label = "**Healthy Work Environment in the Organisation**") %>% 
  modify_caption( "Associations of 'Healthy Work Environment Standards in Organisation' and 'Independent of your present job how satisfied are you with being a registered nurse?' " ) %>% 
  modify_spanning_header( all_stat_cols() ~ labels$satisfied_nurse ) 


```


- Unit 


```{r}

dta %>% 
  select(all_of(dim__scales_unit), satisfied_nurse) %>% 
  mutate(across(where(is.labelled), as_factor)) %>% 
  tbl_summary( by = satisfied_nurse,
               type = everything()~"continuous",
               missing = "no"
               ) %>% 
  add_p() %>% 
    modify_header(label = "**Healthy Work Environment in the Unit**") %>% 
  modify_caption( "Associations of 'Healthy Work Environment Standards in Unit' and 'Independent of your present job how satisfied are you with being a registered nurse?' " ) %>% 
  modify_spanning_header( all_stat_cols() ~ labels$satisfied_nurse ) 


```

### A2. How likely are you to advice a qualified individual to pursue a career in Nursing?


- Organisation 

```{r}

dta %>% 
  select(all_of(dim__scales_org), advice_nurse) %>% 
  mutate(across(where(is.labelled), as_factor)) %>% 
  tbl_summary( by = advice_nurse,
               type = everything()~"continuous",
               missing = "no"
               ) %>% 
  add_p() %>% 
    modify_header(label = "**Healthy Work Environment in the Organisation**") %>% 
  modify_caption( "Associations of 'Healthy Work Environment Standards in Organisation' and 'How likely are you to advice a qualified individual to pursue a career in Nursing?' " ) %>% 
  modify_spanning_header( all_stat_cols() ~ labels$advice_nurse ) 


```


- Unit 


```{r}

dta %>% 
  select(all_of(dim__scales_unit), advice_nurse) %>% 
  mutate(across(where(is.labelled), as_factor)) %>% 
  tbl_summary( by = advice_nurse,
               type = everything()~"continuous",
               missing = "no"
               ) %>% 
  add_p() %>% 
    modify_header(label = "**Healthy Work Environment in the Unit**") %>% 
  modify_caption( "Associations of 'Healthy Work Environment Standards in Unit' and 'How likely are you to advice a qualified individual to pursue a career in Nursing?' " ) %>% 
  modify_spanning_header( all_stat_cols() ~ labels$advice_nurse ) 

```



### A3. How would you describe the quality of care for patients in your unit? 

- Organisation 

```{r}

dta %>% 
  select(all_of(dim__scales_org), quality_care) %>% 
  mutate(across(where(is.labelled), as_factor),
         quality_care = fct_drop(quality_care)
         ) %>% 
  tbl_summary( by = quality_care,
               type = everything()~"continuous",
               missing = "no"
               ) %>% 
  add_p() %>% 
    modify_header(label = "**Healthy Work Environment in the Organisation**") %>% 
  modify_caption( "Associations of 'Healthy Work Environment Standards in Organisation' and 'How would you describe the quality of care for patients in your unit?' " ) %>% 
  modify_spanning_header( all_stat_cols() ~ labels$quality_care ) 


```


- Unit 


```{r}

dta %>% 
  select(all_of(dim__scales_unit), quality_care) %>% 
  mutate(across(where(is.labelled), as_factor),
         quality_care = fct_drop(quality_care)) %>% 
  tbl_summary( by = quality_care,
               type = everything()~"continuous",
               missing = "no"
               ) %>% 
  add_p() %>% 
    modify_header(label = "**Healthy Work Environment in the Unit**") %>% 
  modify_caption( "Associations of 'Healthy Work Environment Standards in Unit' and 'How would you describe the quality of care for patients in your unit?' " ) %>% 
  modify_spanning_header( all_stat_cols() ~ labels$quality_care ) 

```



## C18 with C4, C5, C14, C15, C16, 

### C4, C5, C14, C16,and Intention to leave

```{r}

dta %>%
  select(plan_leave,
         moral_distress, #c4
         staffing_right, #c5
         value_health_safety, #c14
         evaluate_contrib_hwe, #c16
         
         ) %>% 
  mutate(across(where(is.labelled), as_factor)) %>% 
  tbl_summary(
    by = plan_leave,
    missing = "no"
  ) %>% 
  add_overall() %>% 
  modify_header(label = " ") %>% 
  add_p( test = list(all_categorical() ~ "chisq.test") ) %>% 
  # modify_header(all_stat_cols() ~ "**{level}**",label = "**Healthy Work Environment**") %>% 
  modify_caption( "Associations of 'Intention to leave' and ' ... ' " ) %>% 
  modify_spanning_header( all_stat_cols() ~ labels$plan_leave ) 



```


<br>


### C15. Work Done and `Intention to leave`

<br>


```{r}

dta %>% 
  select(
    plan_leave,
    starts_with("work_done")  #c15
  ) %>% 
    mutate(across(where(is.labelled), as_factor)) %>% 
  tbl_summary(
    by = plan_leave,
    missing = "no"
  ) %>% 
  add_overall() %>% 
  modify_header(label = "At the end of a typical shift, to what degree do you get the following work done?") %>% 
  add_p( test = list(all_categorical() ~ "chisq.test") ) %>% 
  # modify_header(all_stat_cols() ~ "**{level}**",label = "**Healthy Work Environment**") %>% 
  modify_caption( "Associations of 'Intention to leave' and 'At the end of a typical shift, to what degree do you get the following work done?' " ) %>% 
  modify_spanning_header( all_stat_cols() ~ labels$plan_leave ) 
```


